---
title: "farsfunctions"
author: "M. McClendon"
date: "2017-04-23"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{farsfunctions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This package is intended to read in and visualize incidents from the National Highway 
Traffic Safety Administration (NHTSA) Fatality Analysis Reporting System (FARS) data. The package contains five functions. However, 3 are of primary use for interrogating data. Those will be explained below. Please note: package assumes FARS data files in the standard format and naming convention are available in the user's working directory.

## fars_summarize_years
This function returns a monthly summary of incidents. It takes a year in the form of an integer or string as an argument and then uses that value to read in a CSV as a tbl_df for data of that given year and and returns a monthly summary of the observations. Usage below.

```{r, echo = FALSE, message=FALSE}
library(farsfunctions)
library(dplyr)
```
```{r}
fars_summarize_years('2013')
```
## fars_read_years
This function returns the month and year corresponding to each FARS observation. It takes a year in the form of an integer or string as an argument and then uses that value to read in a CSV as a tbl_df for data of that given year and returns the month and year corresponding to each observation. 

```{r}
fars_read_years('2013')
```

## fars_map_state
Return a map plot of incidents. This is a function that takes a state number and year in the form of an integer or string as an argument and then uses that value to generate a map plot of observations for that state and year.

```{r, echo = FALSE}
library(farsfunctions)
library(dplyr)
library(maps)
```
```{r}
fars_map_state(21, 2013)
```
